---
title: "Worst Plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotrix)
library(ggplot2)
library(data.table)
```

```{r, warning=FALSE}
origFile <- read.csv("HFS Service Data.csv")
origFile$simple_race<-as.character(origFile$simple_race)
origFile = subset(origFile, simple_race == "5" |simple_race == "8"| simple_race == "9" | simple_race == "17" | simple_race == "128")
cleanFile <- unique(subset(origFile, select =c(recordID,simple_race)))
x<-table(cleanFile$simple_race)
x <- melt(x)
pie3D(x$value,
      height = .6,
      radius = 0.5,
      theta = 0.3,
      col=rainbow(n=40),
      labels=x$Var1,
      shade = 0.4,
      explode=0.4,
      main="Unique records by race 
      with less than 5 observations. 
      Refer to the Data Dictionary to 
      find out the definition for each race code")
```

This plot is terrible for many reasons. The title is long and vague. Also, it is not only a pie chart but a 3-D pie chart. The height, angle and radius of this pie chart also help make this a hard to read chart. The colors for every section are almost indistinguishable between each other. The labels are internal codes when it should be the definition for that code. Without referencing the data dictionary you can't understand this chart.

```{r}
auto<- read.csv("auto-mpg.csv")

img <- jpeg::readJPEG(source = "car1.jpg")

scatter.smooth(auto$mpg, auto$weight, main="Vroom!")
grid(nx = NULL, ny = NULL,
     lty = 2, col = "gray", lwd = 2)
rasterImage(img, 
            xleft=30, xright=50, 
            ybottom=3500, ytop=5500)
rasterImage(img, 
            xleft=0, xright=17, 
            ybottom=1500, ytop=2500)
```

The title for this chart doesn't add any value to the chart. Same story goes for the images on the top right and bottom left corners. The grid lines should be completely removed and the labels for the axis clarified. 